\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-09-28 paper.tex
old ui and final ui implementation

Unfortunately, the hosting provider Kyoto VR provided us with severely throttles
disk write speeds. Because the backend has to write potentially large amounts of
data to the disk every time a tour is uploaded or edited this becomes a major
bottleneck for the web app's performance. For large tours (bigger than 50 MiB)
this can cause an issue where the Node server takes so long to respond that
Apache thinks it has timed out, and sends an erroneous 504 Gateway Timeout
message~\autocite{rfc7231}. Without access to superuser permissions or a faster
hosting provider there is nothing we can do about this bug. The Node server does
eventually complete the request and respond correctly, so until Kyoto VR can get
a better hosting provider we consider it a minor issue.

@@

@@

>>>>

@@

\subsubsection{Early UI}
\label{sec:earlyUI}

As ideas changed and ARuko became what it is today, the UI also changed
greatly from it's early conception to the final version we used. But
that early UI would prove just as important as the final one, because
it was also how we learned many of the practices and skills we needed in order
to create the UI we settled on.

The early UI was very much a product of ARuko's development; many of it's
elements were created as new features were added. But as more features were
added, it became clear that the UI couldn't consist simply of buttons and 
other basic features provided by Unity. We would need to learn more about 
how to create more interesting and useful UI elements to accomodate for 
our new functionality.

\begin{figure}[h]
	\centering
	\includegraphics[width=1\textwidth]{old-ui.png}
	\caption[A screenshot of our early UI]
	{A screenshot of our early UI}
	\label{fig:oldUI}
\end{figure}

Pictured in Figure~\ref{fig:oldUI} is our early UI. It was a very minimal UI,
but still covered all of the uses for our app at the time. The top of the 
screen had two dropdown menus. The one on the left, shown open, would
show AR image targets in the area that users could look for and scan. The right
dropdown would be dynamically populated in each region with buttons bearing  
different images. These images were ones that Atticus wanted to be viewable in AR using ground plane
detection. When tapped, each button would create a 3D Cube, with the given image
on each face, and place it on the ground where the user was pointing.

Learning to create these dropdown menus proved to be a very important lesson
later on, since we would put that exact knowledge to use multiple times in the
final UI. We were able to create the dynamically populated dropdown menus by 
creating an empty vertical layout group, and then using a script to create
buttons for each image based on which region the user is in, and then assign
them as children of the layout group. Then, to get the smooth open/close animation,
we used a boolean to mark the menu as open or closed and had the menu lerp to the
corresponding position each frame until it was fully open or closed.

In between these two dropdown menus is a panel that is shown empty, but in practice would
display the name for the region the user is in at the time. The empty space
in the middle of the screen is where the AR camera display would be shown. In this 
implementation, the AR functionality was the focus of the app, so it made sense
to display the AR camera feed at all times. Lastly, on the bottom is the audio slider for the audio file played in each region. 
We learned a lot about how audio sliders work in Unity with this feature, and would
expand a lot on that knowledge for the final version of the app in order to optimize
the slider's functionality and usefulness.

This early UI taught us a lot about how to make a UI in Unity. We learned a lot of 
basic things, like how all of the UI elements go on the Canvas, which represents
the phone screen, and that everything should be anchored to locations on the screen
so that they stay in the right place despite changes in screen size. 
We also learned more complicated skills that would help us a lot later. We learned
how to use audio sliders, and the ins and outs of how they work. And we learned
how to create dropdown menus that expand when opened and contract when closed, 
creating a very smooth movement affect without needing to animate the component. 
And we also learned how to create button functionality through script, allowing
for UI elements that can changed between the different tours loaded into our app.
And we would bring all of these important skills we learned into the creation
of our final UI to help make it as useful and interesting as it is now.

@@

\subsubsection{Final UI Implementation}
\label{sec:finalUI}

While the newly proposed UI by Atticus was certainly a huge step up from
our previous one, the things we had learned the first time around helped
a lot in overcoming this rather large request in the relatively short amount
of time we had. We had to get much more creative with how we implemented the
UI and how everything worked together, but in the end this allowed us to 
create a rather impressive final UI for and app that we're proud of.

One of the first major challenges we had to tackle was the need to switch
modes while keeping certain UI elements constant. So when a user goes from
the home screen to the Route Map, or into AR Mode, we needed the mode buttons,
audio components, and region info to remain. We went did this by splitting up
screen space into panels, with one for the region info up top, one each for the
mode buttons and audio components on the bottom, and one for the different 
modes in the middle of the screen. Then, within the mode panel, each mode 
screen would be assigned as children, and toggled active or inactive based on 
which mode the user is in at the time. That way, on-screen content can change
while important UI elements remain constant.

Now, within the mode problem itself, there were other important things to 
consider. One such topic was how to handle AR Mode. Previously, we had just
left the AR camera running at all times, since it was the primary feature of 
the app. But now, the focus was much more on the images and audio transcription
in each region. For this, we found that we were able to disable and re-enable
the AR camera in script, so we could turn it off while other modes were the
focus, and back on when needed. We also weren't sure at first what to do about
the chapter select menu, as it was also content that would occupy the space of
the mode panel on screen, but needed to be accessible anywhere via the top 
panel. Using our experience creating dropdown menus in the early UI, we simply
left the chapter select menu enabled at all times, and lerped it open or closed
as needed.

Another group of challenges were created by the content of the main screen,
which showed the images and audio transcript associated with each region. To 
display the images, we wanted the user to be able to click through them like
an image gallery, but weren't sure how to do so in a way that was smooth and
looked nice. But once again, our experience with dropdown menus came in handy. 
We created the gallery out of a horizontal layout group, populated it with 
images dynamically in each region, and then had the buttons lerp the gallery
to different positions in order to switch between each image in a smooth and 
pleasing way. As for the audio transcript, we knew we needed a scrollable
text field that could accomodate varying amounts of text, since the audio files
varied so greatly in length. After doing some research, we found a way to use 
a vertical layout group to create a text field that expanded vertically, within
a predefined bounds, to fit any amount of text provided to it.

At first, our route map screen was rather simple. It was just a static image
of the map, with the route drawn on it, that the user could scroll up and down,
since the image was too tall for the screen. But because the map was so zoomed
out, certain features and text on the map were hard to see. This could also 
make it hard to tell where someone is on the route. So we needed a way to zoom
in on the map and scroll around it, even though Unity doesn't provide this 
relatively common functionality in a standard way. After doing some research, 
were able to write a script that used some of Unity's Input library to get
touch input and use it to zoom in and out on the map within a predefined 
bounds.

The last major UI implementation obstacle we had to overcome was a way to keep
audio playing with the phone in your pocket. Atticus insisted that this sort of
feature was required so that users could listen to the audio tour without using
any of the other functionality the app provides, like the image gallery in each
region or the AR features. But despite how common it is for apps to play audio 
in the background or while the phone is locked , Unity does not provide a way 
to accomplish this either. The way we got around this was by figuring out a way
to prevent UI elements from accidentally being triggered while the phone is 
still unlocked and in the app in the user's pocket. We added a mode to the mode
panel that consists of simply a high opacity black screen with a slider on it,
and added a button to the chapter select dropdown in order to trigger this 
mode. What this pocket mode does is that, because of where it is placed in the 
Unity hierarchy, when it is enabled, it blocks input to all other active UI
components. Then the slider works much like the slider on old Apple devices,
where you slide it from one end to the other to "unlock" the app again, 
re-enabling UI interaction. We figured that it would be rather difficult to 
accidentally trigger the slider while the phone is in one's pocket, and even
have the slider reset if it is only slided partially before letting go.

The rest of the final UI consisted primarily of standard UI features, like 
different basic buttons and panels in different places throughout the app. 
We were ultimately able to replicate Atticus's Adobe XD file almost 
perfectly, allowing us to use a great UI for this app we've worked so hard on.
